Arcturus: efficient proofs for confidential transactions

### 2020-09-17 paper/iacr.tex
Updated security proof

We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$:
$$\sum_{j=0}^m i_j n^j = i$$
This notation will be specified explicitly where confusion may occur.

\section{Protocol: linkable one-of-many commitment}
We wish to build a linkable ring signature construction, where a signer who knows the opening of a commitment may sign messages using an anonymity set containing other commitments for which the signer does not know openings.
Included with the proof of knowledge, the signer also provides a linking tag that is the image of the signing commitment's opening under a verifiable pseudorandom function, using the method of \cite{dodis} that has previously appeared in \cite{omniring,rct3}.
Part of the soundness of the proving system relies on the proper construction of this linking tag.
Upon receipt, a verifier can check whether the linking tag has previously appeared in any other valid proof; if it has not, injectivity assures the verifier that no other signature has been produced by the (unknown) signer.

More specifically, we modify the construction of Bootle \cite{bootle}, which itself is a generalization of a construction by Groth \cite{groth}.
We produce a sigma protocol for the following relation:
$$\mathcal{R}_{\text{link}} = \left\{ \{M_i\}_{i=0}^{N-1} \subset \G, J \in \G ; (l \in \mathbb{Z},r \in \F) : M_l = rG \text{ and } U = rJ \right\}$$
Figures \ref{fig:link} and \ref{fig:link_2} describe the protocol.

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{P}_{\text{link}}(\{M_i\},J;(l,r)):}$
\begin{itemize}
\item Select random $r_A \in \F$ and $\left\{a_{j,i}\right\}_{i=1,j=0}^{n-1,m-1} \subset \F$.
Set $$\{a_{j,0}\}_{j=0}^{m-1} \equiv -\sum_{i=1}^{n-1} a_{j,i}$$ and define $A \equiv \com(a,r_A)$.
\item Define $\left\{\sigma_{j,i}\right\}_{i,j=0}^{n-1,j-1} \subset \F$ such that $\sigma_{j,i} \equiv \delta\left(l_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
Define $B \equiv \com(\sigma,r_B)$.
\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
\item Define coefficients $\left\{p_{k,j}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}x + a_{j,k} \right) = \delta\left(l,k\right)x^m + \sumj p_{k,j}x^j$$ for all $k \in [0,N)$ (using our decomposition notation).
\item Select random $\left\{\rho_j\right\}_{j=0}^{m-1} \subset \F$.
\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}M_k + \rho_jG$$
\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}+ \rho_jJ$$
\end{itemize}

$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
$A,B,C,D,\{X_j\},\{Y_j\}$ \\

$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
$\xi \in \{0,1\}^*$ \\

$\underline{\mathcal{P}(\xi):}$
\begin{itemize}
\item Define $\left\{f_{j,i}\right\}_{i=1,j}^{n-1,m-1}$ such that $f_{j,i} \equiv \sigma_{j,i}\xi + a_{j,i}$.
\item Define $z_A \equiv r_A + \xi r_B$ and $z_C \equiv \xi r_C + r_D$.
\item Define $z \equiv r \xi^m - \sumj \rho_j \xi^j$.
\end{itemize}

$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
$\{f_{j,i}\}_{j=0,i=1}^{m-1,n-1},z_A,z_C,z$
\end{minipage}}
\caption{Sigma protocol for $\mathcal{R}_{\text{link}}$}
\label{fig:link}
\end{figure}

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{V}_{\text{link}}(\{M_i\},J):}$
\begin{itemize}
\item For $0 \leq j < m$, let $f_{j,0} \equiv \xi - \sum_{i=1}^{n-1} f_{j,i}$.
\item Accept if and only if:
\begin{eqnarray}
A + \xi B &=& \com(f,z_A) \label{eqn:ab} \\
\xi C + D &=& \com(f(\xi-f),z_C) \label{eqn:cd} \\
\sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG &=& 0 \label{eqn:x} \\
U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ &=& 0 \label{eqn:y}
\end{eqnarray}
\end{itemize}
\end{minipage}}
\caption{Sigma protocol for $\mathcal{R}_{\text{link}}$ (continued)}
\label{fig:link_2}
\end{figure}

Observe that this protocol can be made non-interactive using the Fiat-Shamir heuristic, where the verifier challenge is produced using a collision-resistant hash function (modeling a random oracle) and the proof transcript \cite{fiatshamir}.

We will show that the sigma protocol is complete, sound, and zero-knowledge, the precise definitions of which are common and found in \cite{groth}.
Informally, we require the protocol be:
\begin{itemize}
\item \textit{Perfectly complete}: Given knowledge of a witness to a statement in the proof relation, an honest prover can always convince an honest verifier of the validity of the witness.
\item \textit{Special sound}: Given a statement in the proof relation, if a prover can answer multiple verifier challenges correctly, then it is possible to extract a witness for this statement.
\item \textit{Special honest-verifier zero knowledge}: Given any statement and verifier challenge, it is possible to simulate a transcript that is accepted by an honest verifier without knowledge of a corresponding witness.
\end{itemize}

\begin{theorem}
The protocol in Figures \ref{fig:link} and \ref{fig:link_2} is perfectly complete, special honest-verifier zero knowledge, and $(m+1)$-special sound.
\end{theorem}

\begin{proof}
The proof follows similarly to that of \cite{bootle}.

% Completeness
We first show perfect completeness.
Suppose the verifier receives a proof generated by an honest prover.
Equation \ref{eqn:ab} holds using the identity $$\sumi \sigma_{j,i} = 1$$ for all $0 \leq j < m$.
Equation \ref{eqn:cd} follows similarly, using the identity $$\left(\sigma_{j,i}\right)^2 = \sigma_{j,i}$$ for all $0 \leq j < m$.
To show Equation \ref{eqn:x} holds:
\begin{eqnarray*}
&& \sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG \\
&=& \sumk M_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}M_k + \rho_jG \right) - zG \\
&=& \sumk M_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jG - zG \\
&=& \sumk M_k \xi^m \delta(l,k) - \sumj \xi^j \rho_jG - \left( r\xi^m - \sumj \rho_j\xi^j \right)G \\
&=& \xi^mrG - \sumj \xi^j \rho_jG - \xi^mrG + \sumj \xi^j \rho_jG \\
&=& 0
\end{eqnarray*}
Equation \ref{eqn:y} follows similarly:
\begin{eqnarray*}
&& U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ \\
&=& U \sumk p_k(\xi) - \sumj \xi^j \left( U \sumk p_{k,j} + \rho_jJ \right) - zJ \\
&=& U \sumk \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jJ - zJ \\
&=& U \sumk \xi^m \delta(l,k) - \sumj \xi^j \rho_jJ - \left( r\xi^m - \sumj \rho_j\xi^j \right)J \\
&=& \xi^mU - \sumj \xi^j \rho_jG - \xi^mrJ + \sumj \xi^j \rho_jG \\
&=& 0
\end{eqnarray*}
since $J = r^{-1}U$ in a valid proof.
Hence the protocol is perfectly complete.

% SHVZK
We next show that the protocol is special honest-verifier zero knowledge.
To do so, we construct a simulator that, given a random verifier challenge $\xi$, can construct a proof transcript with identical distribution to a valid proof.

First, observe that the simulator presented in the proof of Lemma 1 in \cite{bootle} translates identically to our setting.
If the simulator chooses $B \in \G$ uniformly at random, the cited lemma assures us a valid simulation of the proof elements $A,C,D,z_A,z_C,\{f^{(u)}_{j,i \neq 0}\}$; we may compute each $f^{(u)}_{j,0}$ from this.
Further, in a valid proof, $B$ is independent and uniformly distributed as well.

The proof elements $\{X_j\}_{j=1}^{m-1}$ and $\{Y_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof since the set $\{\rho_j\}$ is random and the discrete logarithm problem in $\G$ is hard, so the simulator may choose these uniformly at random.
The verification checks require that $X_0$ and $Y_0$ be uniquely determined by the other elements in the corresponding sets in both real proofs and by the simulator.

Finally, $z$ is uniformly distributed in valid proofs given random $\xi$, so the simulator may choose it uniformly at random.
Hence the construction is special honest verifier zero-knowledge.

% Soundness
It remains to show that the protocol is $(m+1)$-special sound, where $m > 1$.
To show this, we construct an extractor that, given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness.

Suppose that for a given statement, we have a set of $m+1$ distinct verifier challenges $\{\xi_e\}_{e=0}^m$ corresponding to unique valid responses of this form:
$$\left\{ \{f^{(e)}_{j,i}\}, \{z_e\} \right\}_{e=0}^m$$
From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma_{j,i}\}_{j,i=0}^{m-1,n-1}$ and $\{a_{j,i}\}_{j,i=0}^{m-1,n-1}$, and the Pedersen binding property ensures that (with high probability) we have:
$$f^{(e)}_{j,i} = \sigma_{j,i}\xi_e + a_{j,i}$$
for all $e \in [0,m]$.
Using the extracted values, compute
$$p_k(\xi) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}\xi + a_{j,k} \right)$$
for all $k \in [0,N)$.
Extraction of $\{\sigma_{j,i}\}_{j,i=0}^{m-1,n-1}$ immediately yields the signing index $l$.

We have seen that $p_k$ is of degree $m$ only when $k = l$.
Hence there exist coefficients $\{\overline{X}_j,\overline{Y}_j\}_{j=0}^{m-1}$, computed uniquely from the statement and extracted values, such that Equations \ref{eqn:x} and \ref{eqn:y} are of the following form:
\begin{eqnarray*}
\xi^m M_l + \sumj \xi^j\overline{X}_j &=& zG \\
\xi^m U + \sumj \xi^j\overline{Y}_j &=& zJ \\
\end{eqnarray*}

>>>>

We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$:
$$\sum_{j=0}^{m-1} i_j n^j = i$$
This notation will be specified explicitly where confusion may occur.

\subsection{Sigma protocols}
For a given relation $\mathcal{R}$, a sigma protocol for $\mathcal{R}$ is an interactive challenge-response protocol between a prover and verifier, where the prover wishes to convince the verifier it knows a witness corresponding to a statement in $\mathcal{R}$.

A sigma protocol is complete, sound, and zero-knowledge.
These definitions are well known and found, for example, in \cite{groth}.
Essentially, these properties are:
\begin{itemize}
\item \textit{Perfectly complete}: For a witness to a statement in $\mathcal{R}$, an honest prover always convinces an honest verifier of the validity.
\item \textit{Special sound}: Given a statement in $\mathcal{R}$, if the prover can produce valid proof transcripts in response to multiple verifier challenges, then it is possible to extract a witness for the statement from the transcripts.
\item \textit{Special honest-verifier zero knowledge}: Given a statement and known verifier challenge, it is possible to produce a simulated transcript without knowledge of a corresponding valid witness.
\end{itemize}
Sigma protocols can be made non-interactive by replacing random verifier challenges with hash-based transcript challenges under the random oracle model; this approach is called the Fiat-Shamir heuristic \cite{fiat}.

\subsection{Hardness assumption}
We now define a novel cryptographic hardness assumption that is used later to show the soundness of our construction.

\begin{definition}[Dual-target discrete logarithm problem]
\label{def:dual}
Let $\G$ be a group in which the discrete logarithm problem is hard, and let $\F$ be its scalar field.
Let $n > 0$.
Consider the following game between a challenger and a probabilistic polynomial-time player $\A$:
\begin{itemize}
\item The challenger chooses $G,H \in \G$ uniformly at random and sends both to $\A$.
\item $\A$ chooses and returns sets $\{G_i\}_{i=0}^{n-1},\{H_i\}_{i=0}^{n-1} \subset \G$ to the challenger.
\item The challenger chooses a set $\{\mu_i\}_{i=0}^{n-1} \subset \F$ uniformly at random and sends it to $\A$.
\item $\A$ chooses and returns a set $\{x_i\}_{i=0}^{n-1} \subset \F$ to the challenger.
\end{itemize}
We say that $\A$ wins the $(n,\epsilon,t)$-dual-target discrete logarithm game if, in time less than $t$ and with probability at least $\epsilon$, the following are true:
\begin{itemize}
\item $\sumi \mu_i \left( G_i - x_iG \right) = 0$
\item $\sumi \mu_i \left( H - x_iH_i \right) = 0$
\item There exists an index $0 \leq i < n$ such that either $x_iG \neq G_i$ or $x_iH_i \neq H$.
\end{itemize}
\end{definition}

\section{Proving system}
We now present a sigma protocol for the following relation:
\begin{multline*}
\mathcal{R} \equiv \Bigg\{ \{M_i\}_{i=0}^{N-1},\{P_i\}_{i=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \\
M_{l^{(u)}} = r^{(u)}G \; \forall \: u \in [0,w) \text{ and } r^{(u)}J^{(u)} = U \; \forall \: u \in [0,w) \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
\end{multline*}
This captures the necessary elements for transaction authorization, which we describe later; knowledge of signing keys $\{r^{(u)}\}$ will show that the prover has signing authority for inputs to a transaction, and knowledge of the secret key $y$ to an amount commitment difference will show that the transaction amounts balance.
Finally, comparison of the verifiable random function used to produce $\{J^{(u)}\}$ will be used to prevent attempts to sign for the same secret key without revealing the corresponding public key, which is important for signer ambiguity and double-spend protection within or between proofs.

Figures \ref{fig:sigma} and \ref{fig:sigma2} describe the prover and verifier interaction.
Next, we prove that the prover and verifer routines constitute a sigma protocol that is perfectly correct, special sound, and special honest-verifier zero knowledge.

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{P}:}$
\begin{itemize}
\item Select random $r_A \in \F$ and $\left\{a_{j,i}^{(u)}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1} \subset \F$.
Set $$\{a_{j,0}^{(u)}\}_{j,u=0}^{m-1,w-1} \equiv -\sum_{i=1}^{n-1} a_{j,0}^{(u)}$$ and define $A \equiv \com(a,r_A)$.
\item Define $\left\{\sigma_{j,i}^{(u)}\right\}_{i,j,u=0}^{n-1,m-1,w-1} \subset \F$ such that $\sigma_{j,i}^{(u)} \equiv \delta\left(l_j^{(u)},i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
Define $B \equiv \com(\sigma,r_B)$.
\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
\item For $0 \leq u < w$, define coefficients $\left\{p_{k,j}^{(u)}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k^{(u)}(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}^{(u)}x + a_{j,k}^{(u)} \right) = \delta\left(l^{(u)},k\right)x^m + \sumj p_{k,j}^{(u)}x^j$$ (using our decomposition notation).
Then define $p_{k,j} \equiv \sumu p_{k,j}^{(u)}$ and $p_k(x) \equiv \sumu p_k^{(u)}(x)$ accordingly.
\item Select random $\left\{\rho_j\right\}_{j,u=0}^{m-1,w-1}, \left\{\overline{\rho}_j^{(u)}\right\}_{j,u=0}^{m-1,w-1} \subset \F$.
\item Define aggregation coefficients $\{\mu_k\}_{k=0}^{N-1}$ using a $k$-indexed $\hs$ operation, containing all Fiat-Shamir transcript public parameters and proof elements.
\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}\mu_kM_k + \sumu \rho_j^{(u)}G$$
\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}\mu_k + \sumu \rho_j^{(u)}J^{(u)}$$
\item Define $\{Z_j\}_{j=0}^{m-1} \subset \G$ such that: $$Z_j \equiv \sumk p_{k,j}P_k + \sumu \overline{\rho}_j^{(u)}G$$
\end{itemize}

$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
$A,B,C,D,\{X_j\},\{Y_j\},\{Z_j\}$
\end{minipage}}
\caption{Sigma protocol for $\mathcal{R}$}
\label{fig:sigma}
\end{figure}

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
$\xi \in \{0,1\}^*$ \\

$\underline{\mathcal{P}(\xi):}$
\begin{itemize}
\item Define $\left\{f_{j,i}^{(u)}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1}$ such that $f_{j,i}^{(u)} \equiv \sigma_{j,i}^{(u)}\xi + a_{j,i}^{(u)}$.
\item Define $z_A \equiv r_A + \xi r_B$ and $z_C \equiv \xi r_C + r_D$.
\item Define $\left\{z_R^{(u)}\right\}_{u=0}^{w-1} \subset \F$ such that: $$z_R^{(u)} \equiv \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho_j^{(u)}\xi^j$$
\item Define: $$z_S \equiv \xi^m \left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right) - \sumj \left( \xi^j \sumu \overline{\rho}_j^{(u)} \right)$$
\end{itemize}

$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
$\{f_{j,i}^{(u)}\}_{j=0,i=1,u=0}^{m-1,n-1,w-1},z_A,z_C,\{z_R^{(u)}\},z_S$ \\

$\underline{\mathcal{V}:}$
\begin{itemize}
\item For $0 \leq u < w$ and $0 \leq j < m$, set: $$f_{j,0}^{(u)} \equiv \xi - \sum_{i=1}^{n-1} f_{j,i}^{(u)}$$
\item Accept if and only if:
\begin{eqnarray}
A + \xi B &=& \com(f,z_A) \label{eqn:ab} \\
\xi C + D &=& \com(f(\xi-f),z_C) \label{eqn:cd} \\
\sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jX_j - \sumu z_R^{(u)}G &=& 0 \label{eqn:x} \\
U \sumk \mu_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jY_j - \sumu z_R^{(u)}J^{(u)} &=& 0 \label{eqn:y} \\
\sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jZ_j - \xi^m\sum_{j=0}^{T-1} Q_j - z_SG &=& 0 \label{eqn:z}
\end{eqnarray}
\end{itemize}
\end{minipage}}
\caption{Sigma protocol for $\mathcal{R}$ (continued)}
\label{fig:sigma2}
\end{figure}

\section{Security}
\begin{theorem}
The sigma protocol in Figures \ref{fig:sigma} and \ref{fig:sigma2} reflects the relation $\mathcal{R}$ and is perfectly correct, $(m+1)$-special sound, and special honest-verifier zero knowledge.
\end{theorem}

\begin{proof}
The proof proceeds similarly to that of \cite{triptych}, which in turn follows the methods in \cite{groth,bootle}.

To show the protocol is perfectly complete, suppose a verifier receives an honest proof.
We wish to show that all verifier equations hold.

To show that Equation \ref{eqn:ab} holds, observe that since
\begin{eqnarray*}
A + \xi B &=& \com(a + \xi\sigma,r_A + \xi r_B) \\
&=& \com(a + \xi\sigma,z_A),
\end{eqnarray*}
it suffices to show that $f_{j,i}^{(u)} = a_{j,i}^{(u)} + \xi\sigma_{j,i}^{(u)}$ for all $0 \leq i < n$ and $0 \leq j < m$ and $0 \leq u < w$.
If $i \neq 0$, then this equation holds by definition of $f_{j,i}^{(u)}$.
The case $i = 0$ proceeds differently.
To show it, we will use the fact that $$\sumi \sigma_{j,i}^{(u)} = 1$$ for all $0 \leq j < m$ and $0 \leq u < w$ by construction:
\begin{eqnarray*}
f_{j,0}^{(u)} &=& \xi - \sum_{i=1}^{n-1} f_{j,i}^{(u)} \\
&=& \xi - \sum_{i=1}^{n-1} \left( a_{j,i}^{(u)} + \xi\sigma_{j,i}^{(u)} \right) \\
&=& \xi - \sum_{i=1}^{n-1} a_{j,i}^{(u)} - \xi\sum_{i=1}^{n-1} \sigma_{j,i}^{(u)} \\
&=& \xi + a_{j,0}^{(u)} - \xi\left( 1 - \sigma_{j,0}^{(u)} \right) \\
&=& a_{j,0}^{(u)} + \xi\sigma_{j,0}^{(u)}
\end{eqnarray*}

We now show that Equation \ref{eqn:cd} holds.
Since
\begin{eqnarray*}
\xi C + D &=& \com(\xi a(1 - 2\sigma) - a^2,\xi r_C + r_D) \\
&=& \com(\xi a(1 - 2\sigma) - a^2,z_C),
\end{eqnarray*}
it suffices to show that $$f_{j,i}^{(u)}\left( \xi - f_{j,i}^{(u)} \right) = \xi a_{j,i}^{(u)}\left( 1 - 2\sigma_{j,i}^{(u)} \right) - \left(a_{j,i}^{(u)}\right)^2$$ for all $0 \leq i < n$ and $0 \leq j < m$ and $0 \leq u < w$.
We use our previous work and the fact that each $\left(\sigma_{j,i}^{(u)}\right)^2 = \sigma_{j,i}^{(u)}$ since $\sigma_{j,i}^{(u)} \in \{0,1\}$:
\begin{eqnarray*}
f_{j,i}^{(u)}\left( \xi - f_{j,i}^{(u)} \right) &=& \left( a_{j,i}^{(u)} + \xi\sigma_{j,i}^{(u)} \right)\left( \xi - a_{j,i}^{(u)} - \xi\sigma_{j,i}^{(u)} \right) \\
&=& a_{j,i}^{(u)}\xi - \left(a_{j,i}^{(u)}\right)^2 - 2a_{j,i}^{(u)}\xi\sigma_{j,i}^{(u)} + \left( \xi^2\sigma_{j,i}^{(u)} - \xi^2\left(\sigma_{j,i}^{(u)}\right)^2 \right) \\
&=& a_{j,i}^{(u)}\xi - \left(a_{j,i}^{(u)}\right)^2 - 2a_{j,i}^{(u)}\xi\sigma_{j,i}^{(u)} + \left( \xi^2\left(\sigma_{j,i}^{(u)}\right)^2 - \xi^2\left(\sigma_{j,i}^{(u)}\right)^2 \right) \\
&=& \xi a_{j,i}^{(u)}\left( 1 - 2\sigma_{j,i}^{(u)} \right) - \left(a_{j,i}^{(u)}\right)^2
\end{eqnarray*}

Next, we show that Equation \ref{eqn:x} holds:
\begin{eqnarray*}
&& \sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj \xi^jX_j - \sumu z^{(u)}_RG \\
&=& \sumk \mu_kM_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}\mu_kM_k + \sumu \rho^{(u)}_jG \right) - \sumu z^{(u)}_RG \\
&=& \sumk \mu_kM_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
&=& \sumk \mu_kM_k \left[ \xi^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj \xi^j \sumu \rho^{(u)}_jG - \sumu\left[ \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho^{(u)}_j\xi^j \right]G \\
&=& \xi^m\sumu \mu_{l^{(u)}}r^{(u)}G - \sumj \xi^j \sumu \rho^{(u)}_jG - \xi^m\sumu \mu_{l^{(u)}}r^{(u)}G + \sumj \xi^j \sumu \rho^{(u)}_jG \\
&=& 0
\end{eqnarray*}

Equation \ref{eqn:y} holds with similar algebra:
\begin{eqnarray*}
&& \sumk \mu_kU \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj \xi^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \mu_kU p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}\mu_kU + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \mu_kU \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \mu_kU \left[ \xi^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \sumu\left[ \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho^{(u)}_j\xi^j \right](r^{(u)})^{-1}U \\
&=& x^m\sumu \mu_{l^{(u)}}U - \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \xi^m\sumu \mu_{l^{(u)}}U + \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U \\
&=& 0
\end{eqnarray*}

Finally, we show that Equation \ref{eqn:z} holds:
\begin{eqnarray*}
&& \sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj \xi^jZ_j - \xi^m\sum_{j=0}^{T-1} Q_j - z_SG \\
&=& \sumk P_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}P_k + \sumu \overline{\rho}^{(u)}_jG \right) - \xi^m\sum_{j=0}^{T-1} Q_j - z_SG \\
&=& \sumk P_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \sumu \overline{\rho}^{(u)}_jG - \xi^m\sum_{j=0}^{T-1} Q_j - z_SG \\
&=& \xi^m\sumu (s^{(u)}G + a_uH) - \sumj \xi^j \sumu \overline{\rho}^{(u)}_jG - \xi^m\sum_{j=0}^{T-1} (t_jG + b_jH) - \xi^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right)G + \\
&& \sumj \xi^j \sumu \overline{\rho}^{(u)}_jG \\
&=& \left( \sumu a_u - \sum_{j=0}^{T-1} b_j \right)H \\
&=& 0
\end{eqnarray*}
Hence, the protocol is perfectly complete.

Next, we show that the sigma protocol is special honest-verifier zero knowledge.
To do so, we construct a simulator that, when given a random verifier challenge $\xi$, can construct a proof transcript with identical distribution to a valid proof.

Observe first that the simulator presented in the proof of Lemma 1 in \cite{bootle} translates nearly identically to our setting, since we can flatten tensor commitments to a matrix structure with the required sum property.
The simulator first chooses $B \in \G$ uniformly at random; then, the cited lemma assures a valid simulation of the proof elements  $A,C,D,z_A,z_C,\{f^{(u)}_{j,i \neq 0}\}$, and from this we may compute $\{f^{(u)}_{j,0}\}$.
In a valid proof, $B$ is also uniformly distributed.

The proof elements $\{X_j\}_{j=1}^{m-1},\{Y_j\}_{j=1}^{m-1}, \{Z_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof since the elements of $\{\rho_j\},\{\overline{\rho}_j\}$ are uniformly distributed and the discrete logarithm problem in $\G$ is hard; hence, the simulator chooses them uniformly at random.
Since the verification checks require that $X_0,Y_0,Z_0$ be uniquely determined by the other elements in the respective sets, they are selected by the simulator in this manner.

Finally, the elements $\{z^{(u)}_R\}_{u=0}^{w-1}$ and $z_S$ are independent and uniformly distributed in valid proofs given a random verifier challenge $\xi$, so the simulator may choose them uniformly at random.
Hence the protocol is special honest verifier zero-knowledge.

We claim that the protocol is $(m+1)$-special sound, where $m > 1$.
To show this, we construct an extractor that, when given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness for the statement.
In particular, we produce a modified witness for the following relation that is based on the information presented in the prover algorithm, where we define aggregation coefficients $\mu_k$ as before:
\begin{multline*}
\mathcal{R}' \equiv \Bigg\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \\
\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sumu \mu_{l^{(u)}} r^{(u)}G \text{ and } \sumu \mu_{l^{(u)}} r^{(u)}J^{(u)} = \sumu \mu_{l^{(u)}} U \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
\end{multline*}
Observe that if we assume that the dual-target discrete logarithm problem is hard in $\G$, extraction of a witness for $\mathcal{R}'$ implies knowledge of a corresponding witness for $\mathcal{R}$; this in turn provides the desired soundness.

Suppose that for a given statement, we have a set of $(m+1)$ distinct verifier challenges $\{\xi_e\}_{e=0}^m$ corresponding to distinct valid responses of this form:
$$\left\{ \{{}_ef^{(u)}_{j,i}\}, \{{}_ez^{(u)}_R\}, {}_ez_S \right\}_{e=0}^m$$
From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ and $\{a^{(u)}_{j,i}\}_{u=0}^{w-1}$, and the Pedersen binding property ensures that (with high probability) we have:
$${}_ef^{(u)}_{j,i} = \sigma^{(u)}_{j,i}\xi_e + a^{(u)}_{j,i} \; \forall \: e \in [0,m]$$
Using the extracted values, compute the polynomial
$$p_k(x) \equiv \sum_{u=0}^{w-1}\left[ \prod_{j=0}^{m-1} \left( \sigma^{(u)}_{j,k}x + a^{(u)}_{j,k} \right) \right]$$
for all $k \in [0,N)$.
Extraction of $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ immediately yields the signing index set $\{l^{(u)}\}_{u=0}^{w-1}$.

We have seen that $p_k$ is of degree $m$ only when $k \in \{l^{(u)}\}_{u=0}^{w-1}$.
Hence there exist sets of coefficients $\{\overline{X}_j,\overline{Y}_j,\overline{Z}_j\}_{j=0}^{m-1}$, computed uniquely from the statement and extracted values, such that Equations \ref{eqn:x}, \ref{eqn:y}, and \ref{eqn:z} are of the following form:
\begin{eqnarray*}
\xi^m \sumu \mu_{l^{(u)}}M_{l^{(u)}} + \sumj \xi^j\overline{X}_j &=& \left( \sumu z^{(u)}_R \right)G \\
\xi^m \sumu \mu_{l^{(u)}}U + \sumj \xi^j\overline{Y}_j &=& \sumu z^{(u)}_RJ^{(u)} \\
\xi^m \sumu P_{l^{(u)}} + \sumj \xi^j\overline{Z}_j - \xi^m \sum_{j=0}^{T-1} Q_j &=& z_SG
\end{eqnarray*}
